Import and process AODV3 Level2 AOD20 from Aeronet

### 2019-07-29 Code/03_import_AOD_V3.Rmd
AERONET daily error

aod_site_sf <- st_as_sf(site_locations_2019, coords = c("lon", "lat"), crs = 4326)
nemia_buff_aea <- readRDS("~/Jdrive/PM/Just_Lab/projects/ECHO_PM/data/intermediate/nemia_buff_aea.rds")
nemia_buff = st_transform(nemia_buff_aea, crs = 4326) 
aod_site_NE <- aod_site_sf[nemia_buff,]  # a sf object for NEMIA
saveRDS(aod_site_NE, here("Intermediate", "aod_site_NE"))
# NEMIA site list
# site_list_NE <- c(aod_site_NE$Site_Name, "MVCO", "LISCO")
site_list_NE <- c(aod_site_NE$Site_Name)
# US site list
# to be done

@@

AOD is projected to 470nm, as expected it correlates with neighbouring AOD 440nm

>>>>

aod_site_sf <- st_as_sf(site_locations_2019, coords = c("lon", "lat"), crs = 4326)
nemia_buff_aea <- readRDS("~/Jdrive/PM/Just_Lab/projects/ECHO_PM/data/intermediate/nemia_buff_aea.rds")
nemia_buff = st_transform(nemia_buff_aea, crs = 4326)

aod_site_NE <- aod_site_sf[nemia_buff,]  # a sf object for NEMIA
saveRDS(aod_site_NE, here("Intermediate", "aod_site_NE"))
# NEMIA site list
# site_list_NE <- c(aod_site_NE$Site_Name, "MVCO", "LISCO")
site_list_NE <- c(aod_site_NE$Site_Name)

# US site list
aeronet_conus_dt <- readRDS("~/Jdrive/PM/Just_Lab/projects/ECHO_PM/data/intermediate/aeronet_conus_dt.rds")

@@

AOD is projected to 470nm globally, as expected it correlates with neighbouring AOD 440nm
